Centrality and Activity for Envolving Networks

### 2013-06-20 network-science/paper.tex
6

%\pgfplotsset{compat=1.6}
\usetikzlibrary{arrows}
\usetikzlibrary{patterns}
\usetikzlibrary{positioning}
\usetikzlibrary{automata}
\usepackage{tikz-3dplot}

\tikzset{ alert/.style={ very thick, draw=red!80, fill=red!20 } }
\tikzset{ fancy/.style={ very thick, draw=blue!80, fill=blue!20 } }
\tikzset{
  dot/.style={
    very thick,circle,draw=black,fill=black,inner sep=0,minimum size=5pt
  }
}
\tikzset { every state/.style={fancy} }
\tikzset {
  general/.style = {
    shorten >=2pt, node distance=2.5cm, on grid, thick,>=stealth', auto
  }
}
\newcommand{\mathhuge}[1]{\mathlarger{\mathlarger{\mathlarger{#1}}}}
% \newcommand{\mathtiny}[1]{\mathsmaller{\mathlarger{\mathlarger{#1}}}}
\numberwithin{equation}{section}
\mathtoolsset{centercolon}

@@

%>>>
%>>>
\title %<<< Title Region
{
	Metrics and Algorithms for Evolving Social Networks
}
\author
{
	Pufan He\\
	\href{mailto:hpfdf@126.com}{hpfdf@126.com}
	\and
	Yichao Zhou\\
	\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com}
	\and
	Qiwei Feng\\
	\href{mailto:gdfqw93@163.com}{gdfqw93@163.com}
	\and
	Yu Yan\\
	\href{mailto:whyvine@hotmail.com}{whyvine@hotmail.com}
	\and
	Qingyang Li\\
	\href{mailto:591527324@qq.com}{591527324@qq.com}
	\and
	Xin Xing\\
	\href{mailto:823291634@qq.com}{823291634@qq.com}
}
\date{}
%>>>

\begin{document}
\maketitle
\newpage
\begin{abstract}
We address the dynamic properties of typical social networks, in which person
is considered as vertex while friendship is considered as edge. We suppose the
evolution of a social network overtime only includes bidirectional new
connections between existing or newly created nodes, and we assume the graph
will evolve as a typical social network. We study the centrality and activity
metrics for nodes in such graphs by regulate a series of reasonable properties
the metrics should satisfy. We then formally define our metrics and give their
mathematical analysis. We have developed a practical based framework to
maintain the evolving network and the algorithm to compute our metrics with
preferable time and space consumption, including historical queries. Finally,
we put the result of experiment with a couple of authentic data.

@@

\section{Introduction}
social network
\section{}
\section{}
\section{Conclusion}

\end{document}

>>>>

\pgfplotsset{compat=1.6}
\usetikzlibrary{arrows}
\usetikzlibrary{patterns}
\usetikzlibrary{positioning}
\usetikzlibrary{automata}
\usepackage{tikz-3dplot}

\tikzset{ alert/.style={ very thick, draw=red!80, fill=red!20 } }
\tikzset{ fancy/.style={ very thick, draw=blue!80, fill=blue!20 } }
\tikzset{
  dot/.style={
    very thick,circle,draw=black,fill=black,inner sep=0,minimum size=5pt
  }
}
\tikzset { every state/.style={fancy} }
\tikzset {
  general/.style = {
    shorten >=2pt, node distance=2.5cm, on grid, thick,>=stealth', auto
  }
}
\newcommand{\mathhuge}[1]{\mathlarger{\mathlarger{\mathlarger{#1}}}}
% \newcommand{\mathtiny}[1]{\mathsmaller{\mathlarger{\mathlarger{#1}}}}
\numberwithin{equation}{section}
\mathtoolsset{centercolon}
\bibliographystyle{plain}

@@

%>>>
%>>>
\title %<<< Title Region
{
	Metrics and Algorithms for Evolving Social Networks
}
\author
{
	Pufan He\\
	\href{mailto:hpfdf@126.com}{hpfdf@126.com}
	\and
	Yichao Zhou\\
	\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com}
	\and
	Qiwei Feng\\
	\href{mailto:gdfqw93@163.com}{gdfqw93@163.com}
	\and
	Yu Yan\\
	\href{mailto:whyvine@hotmail.com}{whyvine@hotmail.com}
	\and
	Qingyang Li\\
	\href{mailto:591527324@qq.com}{591527324@qq.com}
	\and
	Xin Xing\\
	\href{mailto:823291634@qq.com}{823291634@qq.com}
}
\date{}

%>>>

\begin{document}
\maketitle
\newpage
\begin{abstract}
We address the dynamic properties of typical social networks, in which person
is considered as vertex while relation is considered as edge. We suppose the
evolution of a social network overtime only includes bidirectional new
connections between existing or newly created nodes, and we assume the graph
will evolve as a typical social network. We study the centrality and activity
metrics for nodes in such graphs by regulate a series of reasonable properties
the metrics should satisfy. We then formally define our metrics and give their
mathematical analysis. We have developed a practical based framework to
maintain the evolving network and the algorithm to compute our metrics with
preferable time and space consumption, including historical queries. Finally,
we put the result of experiment with a couple of authentic data.

@@

\section{Introduction}
social network 
\section{}
\section{}
\section{Conclusion}
\nocite{*}
\bibliography{paper.bib}
\end{document}
